Assessing glymphatic transport velocities by adjoint methods

### 2018-10-01 tex/paper.tex
text added

\documentclass[11pt,a4paper]{article}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}
\usepackage[table,x11names]{xcolor}
\title{Assessing glymphatic transport velocities by adjoint methods}

@@

The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} which later was found to be particularly active during sleep~\cite{xie2013sleep}. 
It has been proposed that this pathway plays an important role in the waste
clearance of the brain. In particular, since the brain lack a lymphatic system, 
which elsewhere in our body plays a crucial role in waste clearance, the system has been called the glymphatic system~\cite{jessen2015glymphatic}.  
The glymphatic system remains controversial and modeling attempts
has so far mostly failed to explain the biomechanics of the system~\cite{holter2017interstitial, smith2017glymphatic}. A proper biomechanical 
understanding of the pathway has significant potential because
dementia such as Alzheimer´s and Parkinson´s diseases are
associated with accumulation of metabolic waste such as
amyloid-beta and CSF-tau.

In \cite{ringstad2018brain} brainwide distribution of MRI-contrast was demonstrated during 24 hours after lumbar contrast injection. Brain wide distribution by diffusion alone was deemed unlikely by the authors (some of which are part 
of this study as well). The argument was based on analytical considerations where it was calculated that 50\% contrast enrichment would occur after 
55 hours using the error function which is valid for planar diffusion. However, 
the surface of the brain is folded and is around five times larger than 
a corresponding surface of a ball with the same volume. Hence, 
a more rigorous modeling attempt is warrented. Complicating factors
are however that the contrast in the surrounding CSF is heterogenous
and changes significantly during the 24 hours of the investigations. 
Furthermore, images were obtained only at a few time-points during the investigations in \cite{ringstad2018brain}.

Our purpose in this paper is to attempt a more rigorous methodology 
for assessing the apparent diffusion process. To this end we employ
adjoint methods to determine the apparent diffusion coefficient 
that would explain the tracer distribution.

\section{Methodology}

\subsection*{Data}
The data consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected. The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic}.

\begin{figure}
\includegraphics[width=0.95\textwidth]{GMRI.png} 
\label{fig1} 
\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI. Also include a zoom on the region of interest}}
\end{figure}

\subsection*{Mathematical Model}
In order to assess whether the contrast distribution shown 
in Figure \ref{fig1} is governed by a diffusion process we
aim to solve a PDE constrained optimization problem where
the contrast distribution, boundary conditions, and apparent
diffusion coefficition are solved for by optimizing with
respect to the observed contrast distribution.  
The objective function was defined as 
\begin{equation}
\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t 
\label{EQ::objf}
\end{equation}
subject to 
\begin{equation}
\begin{aligned}
\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
\end{aligned}
\label{Eq::PDE}
\end{equation}
Here $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
coefficient, and $g$ is the boundary condition. Furthermore,  
the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient. We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$. The apparent
diffusion constant is assumed constant within the CSF, grey and 
white matter but each region may have different constants.  
The $\alpha$ and $\beta$ parameters are regularization parameters 
and $u_{obs}$ are observations at certain time-points.

\subsection*{Manufactured Solution}
In order to verify our strategy and test the dependency of the
regularization paramters, we perform a test case with a
known solution.  
The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
\begin{equation}
g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
\end{equation}
The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
\begin{equation}
D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
\end{equation}  
The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter. The forward simulation gave a total of 120 possible observation time points. These points 
will be denoted as $\tau$.

@@

\section*{Implementation}
The code used the FEniCS project to sole the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements. The module dolfin adjoint [?] was used to compute the reduced functional, and the optimization used the scipy optimize library to minimize the functional using L-BFGS-B algorithm.

@@

Linear interpolation of the forward problem was used to compute the difference from the observation,

The initial values of the optimization algorithm was chosen to be $1,1,1$. Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.  $D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.

The noise susceptibility was also tested by adding an uniform distribution noise term to the observations. The noise term was constructed using numpy random and multiplied with a noise amplitude. The noise amplitudes were chosen to be $ 5\%, 10\%, 50\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.

@@

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
\hline
\rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\

@@

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
\hline
 1.0e-01 	 & 1.0e+00 	 & 20 & 221 	 & +0.155 & +0.056 & +0.020 & +0.464 \\ 
 1.0e-01 	 & 1.0e-01 	 & 20 & 218 	 & +0.422 & +0.185 & +0.029 & +0.485 \\ 
 1.0e-01 	 & 1.0e-02 	 & 20 & 332 	 & +0.925 & +0.484 & +0.047 & +0.569 \\ 
 1.0e-01 	 & 1.0e-03 	 & 20 & 327 	 & +1.140 & +0.629 & +0.057 & +0.608 \\ 
 1.0e-01 	 & 1.0e-04 	 & 20 & 320 	 & +1.175 & +0.652 & +0.059 & +0.615 \\ 
 1.0e-01 	 & 1.0e-05 	 & 20 & 308 	 & +1.173 & +0.654 & +0.059 & +0.615 \\ 
 1.0e-02 	 & 1.0e+00 	 & 20 & 251 	 & +0.008 & +0.009 & +0.014 & +0.460 \\ 
 1.0e-02 	 & 1.0e-01 	 & 20 & 214 	 & +0.062 & +0.029 & +0.009 & +0.457 \\ 
 1.0e-02 	 & 1.0e-02 	 & 20 & 331 	 & +0.155 & +0.080 & +0.003 & +0.475 \\ 
 1.0e-02 	 & 1.0e-03 	 & 20 & 537 	 & +0.209 & +0.113 & -0.000 & +0.537 \\ 
 1.0e-02 	 & 1.0e-04 	 & 20 & 488 	 & +0.222 & +0.122 & -0.001 & +0.561 \\ 
 1.0e-02 	 & 1.0e-05 	 & 20 & 512 	 & +0.223 & +0.121 & -0.001 & +0.567 \\ 
 1.0e-03 	 & 1.0e+00 	 & 20 & 256 	 & -0.006 & +0.004 & +0.013 & +0.461 \\ 
 1.0e-03 	 & 1.0e-01 	 & 20 & 258 	 & +0.032 & +0.012 & +0.008 & +0.459 \\ 
 1.0e-03 	 & 1.0e-02 	 & 20 & 287 	 & +0.077 & +0.029 & +0.005 & +0.458 \\ 
 1.0e-03 	 & 1.0e-03 	 & 20 & 331 	 & +0.107 & +0.044 & +0.003 & +0.471 \\ 
 1.0e-03 	 & 1.0e-04 	 & 20 & 576 	 & +0.095 & +0.041 & +0.004 & +0.520 \\ 
 1.0e-03 	 & 1.0e-05 	 & 20 & 507 	 & +0.089 & +0.044 & +0.004 & +0.530 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.461 \\ 
 1.0e-04 	 & 1.0e-01 	 & 20 & 315 	 & +0.028 & +0.010 & +0.008 & +0.459 \\ 
 1.0e-04 	 & 1.0e-02 	 & 20 & 396 	 & +0.067 & +0.023 & +0.005 & +0.459 \\ 
 1.0e-04 	 & 1.0e-03 	 & 20 & 242 	 & +0.103 & +0.038 & +0.003 & +0.463 \\ 
 1.0e-04 	 & 1.0e-04 	 & 20 & 207 	 & +0.100 & +0.035 & +0.003 & +0.466 \\ 
 1.0e-04 	 & 1.0e-05 	 & 20 & 457 	 & +0.080 & +0.035 & +0.003 & +0.483 \\ 
 1.0e-05 	 & 1.0e+00 	 & 20 & 215 	 & -0.006 & +0.004 & +0.013 & +0.461 \\ 
 1.0e-05 	 & 1.0e-01 	 & 20 & 244 	 & +0.028 & +0.010 & +0.008 & +0.459 \\ 
 1.0e-05 	 & 1.0e-02 	 & 20 & 399 	 & +0.070 & +0.024 & +0.005 & +0.460 \\ 
 1.0e-05 	 & 1.0e-03 	 & 20 & 267 	 & +0.108 & +0.040 & +0.003 & +0.463 \\ 
 1.0e-05 	 & 1.0e-04 	 & 20 & 361 	 & +0.089 & +0.034 & +0.003 & +0.473 \\ 
 1.0e-05 	 & 1.0e-05 	 & 20 & 298 	 & +0.101 & +0.036 & +0.003 & +0.473 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 240 	 & -0.007 & +0.004 & +0.013 & +0.461 \\ 
 1.0e-06 	 & 1.0e-01 	 & 20 & 269 	 & +0.027 & +0.009 & +0.008 & +0.459 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 314 	 & +0.070 & +0.025 & +0.005 & +0.459 \\ 
 1.0e-06 	 & 1.0e-03 	 & 20 & 214 	 & +0.102 & +0.038 & +0.002 & +0.462 \\ 
 1.0e-06 	 & 1.0e-04 	 & 20 & 437 	 & +0.079 & +0.032 & +0.004 & +0.475 \\ 
 1.0e-06 	 & 1.0e-05 	 & 20 & 353 	 & +0.088 & +0.033 & +0.005 & +0.478 \\ 
\end{tabular}}
\label{Tab::1}
\end{table}

\begin{table}
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. Noise 0.015 amp }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
 1.0e+00 	 & 1.0e+00 	 & 10 & 205 	 & +4.270 & +0.303 & +0.091 & +0.589 \\ 
 1.0e+00 	 & 1.0e-01 	 & 10 & 190 	 & +4.270 & +0.306 & +0.091 & +0.596 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 244 	 & +4.523 & +0.304 & +0.091 & +0.597 \\ 
 1.0e+00 	 & 1.0e-03 	 & 10 & 204 	 & +4.275 & +0.306 & +0.091 & +0.597 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 205 	 & +4.272 & +0.306 & +0.090 & +0.597 \\ 
 1.0e+00 	 & 1.0e-05 	 & 10 & 185 	 & +4.272 & +0.305 & +0.090 & +0.597 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 223 	 & +4.538 & +0.303 & +0.091 & +0.597 \\ 
 1.0e-01 	 & 1.0e+00 	 & 10 & 179 	 & +0.125 & +0.095 & +0.040 & +0.488 \\ 
 1.0e-01 	 & 1.0e-01 	 & 10 & 141 	 & +0.123 & +0.093 & +0.040 & +0.506 \\ 
 1.0e-01 	 & 1.0e-02 	 & 10 & 201 	 & +0.124 & +0.093 & +0.040 & +0.515 \\ 
 1.0e-01 	 & 1.0e-03 	 & 10 & 207 	 & +0.126 & +0.093 & +0.041 & +0.516 \\ 
 1.0e-01 	 & 1.0e-04 	 & 10 & 162 	 & +0.125 & +0.093 & +0.040 & +0.516 \\ 
 1.0e-01 	 & 1.0e-05 	 & 10 & 209 	 & +0.121 & +0.093 & +0.041 & +0.516 \\ 
 1.0e-01 	 & 1.0e-06 	 & 10 & 147 	 & +0.123 & +0.093 & +0.041 & +0.516 \\ 
 1.0e-02 	 & 1.0e+00 	 & 10 & 221 	 & +0.017 & +0.067 & +0.039 & +0.481 \\ 
 1.0e-02 	 & 1.0e-01 	 & 10 & 138 	 & +0.005 & +0.065 & +0.040 & +0.483 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 174 	 & +0.006 & +0.065 & +0.040 & +0.500 \\ 
 1.0e-02 	 & 1.0e-03 	 & 10 & 227 	 & +0.007 & +0.066 & +0.039 & +0.510 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 164 	 & +0.004 & +0.065 & +0.040 & +0.509 \\ 
 1.0e-02 	 & 1.0e-05 	 & 10 & 223 	 & +0.006 & +0.065 & +0.040 & +0.512 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 179 	 & +0.007 & +0.065 & +0.040 & +0.510 \\ 
 1.0e-03 	 & 1.0e+00 	 & 10 & 178 	 & +0.005 & +0.064 & +0.039 & +0.481 \\ 
 1.0e-03 	 & 1.0e-01 	 & 10 & 182 	 & -0.007 & +0.062 & +0.040 & +0.481 \\ 
 1.0e-03 	 & 1.0e-02 	 & 10 & 94 	 & -0.006 & +0.062 & +0.038 & +0.487 \\ 
 1.0e-03 	 & 1.0e-03 	 & 10 & 108 	 & -0.005 & +0.063 & +0.039 & +0.489 \\ 
 1.0e-03 	 & 1.0e-04 	 & 10 & 136 	 & -0.008 & +0.062 & +0.040 & +0.490 \\ 
 1.0e-03 	 & 1.0e-05 	 & 10 & 93 	 & -0.006 & +0.063 & +0.040 & +0.489 \\ 
 1.0e-03 	 & 1.0e-06 	 & 10 & 81 	 & -0.006 & +0.062 & +0.040 & +0.489 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 166 	 & +0.007 & +0.064 & +0.039 & +0.482 \\ 

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}
\usepackage[table,x11names]{xcolor}
\usepackage{geometry}
\title{Assessing glymphatic transport velocities by adjoint methods}

@@

The discovery of the paravascular pathway in 2011~\cite{iliff2012paravascular} propose a novel component
crucial to the metabolism of the brain which may potientially provide an explanation for the accumulation of
waste such as amyloid beta in elderly, ultimately leading to diseases such as Alzheimer and Parkinson. 
In the rest of our body, the lymphatic system plays an important role
in the clearance of metabolic waste, but there are no lymphs within the brain. This fact is puzzling in particular because
the brain requires around 10 times more energy per volume than the result of the body. The paravascular 
pathway is proposed important to waste clearance and has therefore been named the \emph{glymphatic system}.

The pioneering works of Sykov{\'a} and Nicholson~\cite{sykova2008diffusion} demonstrated
that diffusion was a governing transport mechanism in the brain. However, 
the clearance of CSF-tracers during sleep~\cite{xie2013sleep} in mice demonstrated transportation
much faster what could be explained by diffusion and it was proposed that arterial pulsation powered
accelrated perivascular flow combined convective interstitial flow. Several modelling attempts
have put the theory to the test~\cite{asgari2016glymphatic, smith2017glymphatic, holter2017interstitial}, 
but so far computational modeling have failed to adequately described the mechanism.

Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.

Paragraph about timescales etc.

The purpose of this paper is to attempt to assess transportation speed in terms of an apparent diffusion coefficient 
by using adjoint methods provided by \cite{} for optimizing the coefficient with respect to data. As
such a coefficient larger than commonly reported values of diffusion would suggest that at the
timescale of minutes to hours there is indeed a glymphatic transportation which may potentially 
be responsible for metabolic waste.

An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
and the mathematical methodology used for determining the apparent diffusion coefficients.

\section{Methods}

\subsection*{Data}
The data consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected. The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours.

\subsection*{Mathematical Model}
The objective function was defined as 
\begin{equation}
\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t 
\label{EQ::objf}
\end{equation}
subjugated by   
\begin{equation}
\begin{aligned}
\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
\end{aligned}
\label{Eq::PDE}
\end{equation}
with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient. We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.

\section*{Manufactured Solution}
The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
\begin{equation}
g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
\label{EQ::DIRI}
\end{equation}
The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
\begin{equation}
D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
\end{equation}  
The magnitude order of the diffusion coefficient are chosen so that they resemble diffusion coefficient in csf, grey and white matter. The forward simulation gave a total of 120 possible observation time points. These points 
will be denoted as $\tau$.

@@

\section*{Implementation}
The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements. The module dolfin adjoint [?] was used to compute the reduced functional, and the optimization used the scipy optimize library to minimize the functional using L-BFGS-B algorithm.

@@

The times in the forward simulation do not always overlap with observations times. Thus a linear interpolation of the forward problem was used to compute the difference from the observation, i.e 
\begin{equation}
u        d U_prev + \Delta t - dt U.
\end{equation}
Here $dt$ is forward timestep and $\Delta t$ is the difference between ?? 
The initial values of the optimization algorithm was chosen to be $1,1,1$. Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.  $D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.

The noise susceptibility was also tested by adding an uniform distribution noise term to the observations. The noise term was constructed using numpy random and multiplied with a noise amplitude. The noise amplitudes were chosen to be $ 10\%, 50\%, 100\%$ of the maximum initial boundary conditions, so that negative concentrations are avoided.

The real data observations had observation times that had an unevenly distribution over 24 hours. Thus having  constant time between observations is not realsitic. Therefore the number of observation and the unevenly distribution of them will be tested. To accurately depict the real data observations.

@@

\subsection{The relaxation parameters}
The relaxation parameters needs to be calibrated depending on the problem, and thus the diffusion parameters were computed by large range of relaxation parameters values. The results are shown in Tab.\ref{Tab::1}, and it is shown in red that $\alpha=1.0$ have large discrepancy in the parameters values of $D_{\Omega_1}$.

\subsection{The number of timessteps}
The first results focus on the accuracy of the minimization based on the number of time steps. It can be assumed that the error decreases  while the number of time steps increases since the Dirichlet boundary condition in Eq.\ref{EQ::DIRI} are quadratic, while the forward problem is a linear approximation.

This can be seen in Tab.??, Tab.??

In Tab.\ref{Tab::1}, we can see that the

\subsection{The number of observations}
The number of observations can also be considered an important aspect, since the number of observations can be limited. Thus the number of observations set to $5,10 $ and $20$, and

\subsection{The noise susceptibility}

The noise susceptibility can be seen in Tab. ?? and Tab. ??, and we see that a noise amplitude of $10 \%$ does not lead to significant change

The diffusion equation does not pose any difficulties numerically

This method can be adapted to

\newpage 
\newgeometry{top=0.5cm}

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. }
\resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
\hline
\rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\

@@

\begin{table}
\centering
\caption{ tau = double  }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
\hline
 1.0e-05 	 & 1.0e-02 	 & 20 & 429 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 386 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
\end{tabular}}
\label{Tab::2}
\end{table}

\begin{table}
\centering
\caption{ tau = double  }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
\hline
 1.0e-05 	 & 1.0e-03 	 & 40 & 210 	 & +0.019 & +0.005 & -0.001 & +0.002 \\ 
 1.0e-05 	 & 1.0e-01 	 & 40 & 597 	 & +0.006 & +0.015 & -0.008 & +0.017 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 910 	 & +0.046 & +0.047 & -0.020 & +0.065 \\ 
\end{tabular}}
\label{Tab::2}
\end{table}

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. Noise 0.015 amp }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline

\end{tabular}}
\label{Tab::3}
\end{table}

\newpage
\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. Noise 0.03 amp }
\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline
 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
 1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\

 1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\

 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\

 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\

 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
 1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\

 1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
 1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
 1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
 1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
 1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
